---
title: ''
output: html_document
---

---
title: 'Is my local Wisconsin bike shop open?'
output:
  html_document:
    self_contained: false
---
Madison has a lot of bike shops (including mobile bike repair services), as well as a lot of repair stations in public places. Here is a map of all of them. If you have new information or found an error, please email [harald@madisonbikes.org](mailto:harald@madisonbikes.org).

Last update: `r Sys.time()`

```{r echo=FALSE, results=FALSE, message=FALSE}
library(leaflet)
library(googlesheets4)
library(tidyverse)

sheets_deauth()


df <- read_sheet("https://docs.google.com/spreadsheets/d/1TaghQIUjMTDf1R33BtGtUAwIYjfeoHTUf7wJjMg0O6M/edit?ts=5e790c29#gid=1069622854")


shops <- df %>% 
  rename(name = `Shop Name`) %>% 
  mutate(Status = replace_na(Status, "unknown")) %>% 
  mutate(pop = paste0("<b>",name, "</b><br>",
                      "Phone: ", Phone, "<br>",
                      "Website: ", Website, "<br>",
                      "Operating Status: ", Status))
```


```{r echo=FALSE, warning=FALSE}



shops %>% 
  leaflet(width = "90%") %>% 
  addProviderTiles(provider = "Stamen.TonerLite") %>%
  addMarkers(lng = ~Long, lat = ~Lat, popup = ~pop)
```

