---
title: 'Madison Area Bike Shops and Repair Stations'
output: 
  html_fragment
---


Madison and Dane County have a lot of bike shops (including mobile bike repair services), as well as a lot of repair stations in public places. Here is a map of all(?) of them. If you have new information or found an error, please email [harald@madisonbikes.org](mailto:harald@madisonbikes.org). 



```{r echo=FALSE, results=FALSE, message=FALSE, warning=FALSE}
library(leaflet)
library(googlesheets4)
library(tidyverse)
library(sf)

gs4_deauth()

#read sheet with shop info
df <- read_sheet("https://docs.google.com/spreadsheets/d/1qkA4_rs_VMDfjsd42Da_JP_2pchGulRiq_yR2tgXJhM/",
                 col_types = "c-nncci__cccT_")#loading only relevant variables to improve performance

# read repair stations file from City of Madison Open Data portal; URL eventually expires and needs to be updated
# from https://data-cityofmadison.opendata.arcgis.com/datasets/bike-repair-station/
# URL can't be extracted directly anymore, and so you have to download the file and then "copy download link"
# in the Firefox download manager
download.file("https://opendata.arcgis.com/api/v3/datasets/76d43c3b570246bb98d6f44f0400c000_34/downloads/data?format=shp&spatialRefId=4326&where=1%3D1", "data/repair_stations.zip")
unzip("data/repair_stations.zip", exdir = "./data")
file.remove("data/repair_stations.zip")
repair_stations <- st_read("data/Bike_Repair_Station.shp")

repair_stations <- repair_stations %>% 
  mutate(pop = paste0("<b>Repair station</b><br>",Descriptio)) %>% 
  select(pop)


shops <- df %>% 
  rename(name = `Shop Name`) %>% 
  mutate(Status = replace_na(Status, "unknown")) %>% 
  mutate(pop = paste0("<b>",name, "</b><br>",
                      "Address: ", Address, ", ", City, "<br>",
                      "Phone: ", Phone, "<br>",
                      "Website: <a href=\"", Website, "\">", Website, "</a><br>"))
```


```{r echo=FALSE, warning=FALSE}

shop_icon <- makeAwesomeIcon(icon = "bicycle",
                         library = "fa")
repair_icon <- makeAwesomeIcon(icon = "wrench",
                               library = "fa",
                               markerColor = "lightgray")

shops %>% 
  leaflet(width = "90%") %>% 
  addProviderTiles(provider = "OpenStreetMap.Mapnik") %>%
  addAwesomeMarkers(lng = ~Long, lat = ~Lat, popup = ~pop, icon = shop_icon) %>%
  addAwesomeMarkers(data = repair_stations, popup = ~pop, icon = repair_icon, clusterOptions = TRUE)
  
```

Last update: `r Sys.time()`

Data: [City of Madison OpenData Portal (repair stations)](https://data-cityofmadison.opendata.arcgis.com/), Madison Bikes